RSV

### 2018-01-12 Analysis/RSV.Rmd
Moved sliding window analysis to RSV.R

ggplot2.multiplot(plotlist=plots, cols=4)

```{r}
ppxSlidingStrategies = function(c=NULL, y=NULL) {
  if (!is.null(y) && !is.null(c)) {
    stateSlidingOnset = (stateThresholdsByWindow %>% filter(year==y))$onset.median
    stateSlidingOffset = (stateThresholdsByWindow %>% filter(year==y))$offset.median
  }

  list(
    stateSlidingOnset=function(time) {
      evalOnsetStrategy(stateSlidingOnset, time)
    },
    stateSlidingOffset=function(time) {
      evalOffsetStrategy(stateSlidingOffset, time)
    }
  )
}

slidingWindowDuration = 3 # Years

```{r}
stateObsByWindow = dataset %>% 
  mutate(time=weeki) %>% 
  group_by(time, year, weekofyear) %>% 
  summarize(rsv=sum(rsv)) %>%
  as.data.frame()

total = data.frame(time=stateObsByWindow$time, rsv=0)

for (idx in seq(1, slidingWindowDuration)) {
  total = total %>%
    inner_join(stateObsByWindow %>%
                 mutate(time=time + 52 * idx) %>%
                 select(time, rsv),
               by="time"
               ) %>%
    mutate(rsv=rsv.x + rsv.y) %>%
    select(time, rsv)
}

stateObsByWindow = stateObsByWindow %>%
  select(-rsv) %>%
  inner_join(total, by="time") %>%
  group_by(year) %>%
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
  select(-time) %>%
  rename(time=weekofyear) %>%
  filter(year >= min(rsvYears) + slidingWindowDuration) %>%
  as.data.frame()

rsvWindowYears = unique(stateObsByWindow$year)

statePredByWindow = data.frame()
stateThresholdsByWindow = data.frame()

progress = txtProgressBar(max=length(rsvWindowYears), style=3)
idx = 0

for (y in rsvWindowYears) {

  stateYearObs = stateObsByWindow %>% filter(year==y)
  stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)

  stateYearPred = stateYearModel %>% 
    predict(type="response", newdata=modelTime, se.fit=TRUE)

  stateYearPred = modelTime %>% 
    cbind(data.frame(rsv.fit=stateYearPred$fit, rsv.fit.se=stateYearPred$se.fit)) %>%
    cbind(stateYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
    mutate(year=y)

  statePredByWindow = statePredByWindow %>% rbind(stateYearPred)

  stateYearThresholds = stateYearModel %>%
    outbreak.predict.scalars(
      modelTime,
      function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
    ) %>%
    mutate(year=y)

  stateThresholdsByWindow = stateThresholdsByWindow %>% rbind(stateYearThresholds)

  idx = idx + 1
  setTxtProgressBar(progress, idx)
}
```

@@

```{r}
onset = ggplot(stateThresholdsByWindow) +
  geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
  labs(x="RSV Season Onset")
offset = ggplot(stateThresholdsByWindow) +
  geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
  labs(x="RSV Season Offset")

>>>>

ggplot2.multiplot(plotlist=plots, cols=4)
```

@@
